Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-13 tex/nusselt_paper.tex
Not sure the comment on \epsilon -> \inf is correct or critical to our argument; here's a possible replacement.  Is the shock heating significant?
Adding back in solar kappa sentence.

We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of Nu showed little
dependence on depth. By performing a linear stability analysis, we determined that the onset of convection
occurs at Ra$_c$ $= \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^4$Ra$_c$ for $\epsilon = 10^{-7}$.  At
high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  
These shocks heat downflowing material which reduces the efficiency of convective transport.
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
In the context of Fig \ref{fig:ma_v_eps}, it is unsurprising that as $\gamma \rightarrow 1$, systems in which shocks
form are easier to produce \cite{cattaneo&all1990}.  In such a limit, $m_{ad} \rightarrow \infty$ 
and therefore $\epsilon \rightarrow \infty$.

@@

The dynamics of these polytropic solutions are complex and highly time-dependent, even in two dimensions.
Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
\cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
of $\epsilon$ studied here are far below the values found in nature.  If the scalings of Nu and Ma
presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
$\text{Nu }\approx 10^{6}$.

>>>>

We solved initial value problems which start in hydrostatic and thermal equilibrium and experienced infinitesimal 
kicks compared to $\epsilon$ in $T_1$.  Solutions were time-evolved until a long-time average of Nu showed little
dependence on depth. By performing a linear stability analysis, we determined that the onset of convection
occurs at Ra$_c$ $= \{10.06, 10.97, 10.97\}$ for $\epsilon = \{0.5, 10^{-4}, 10^{-7}\}$, respectively.  We study Rayleigh
numbers from values at onset up to nearly $10^6$Ra$_c$ for $\epsilon = 0.5$, $10^5$Ra$_c$ for $\epsilon = 10^{-4}$,
and $10^4$Ra$_c$ for $\epsilon = 10^{-7}$.  At
high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
(Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  
These shocks heat downflowing material which reduces the efficiency of convective transport.
Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
These shocks heat material entering the downflows, reducing both the
buoyant driving and the efficiency of convective transport.

@@

The dynamics of these polytropic solutions are complex and highly time-dependent, even in two dimensions.
Time-dependent oscillating shear states have developed spontaneously, as seen before in RB convection
\cite{goluskin&all2014}.  While computationally difficult, the highest values of Ra and the lowest value
of $\epsilon$ studied here are far below the values found in nature.  If the scalings of Nu and Ma
presented here hold, then under solar conditions ($\text{Ra }\approx 10^{20}$, $\text{Ma }\approx 10^{-4}$), we expect that $\epsilon \approx 10^{-20}$ and
$\text{Nu }\approx 10^{6}$.  
Solar conditions are of course more complicated, as there $\kappa$ is
set by the radiative opacity, which depends on both $\rho$ and $T$.
